Decoding Toronto's Crime Patterns: A Comprehensive Analysis of Victims and Trends (2014-2022)

### 2024-01-24 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Rearrange the paper

---
title: "Decoding Toronto's Crime Patterns: A Comprehensive Analysis of Victims and Trends (2014-2022)"
author: "Chay Park"
date: today
date-format: long
format: pdf
editor: visual
bibliography: references.bib
prefer-html: true
toc: true
toc-depth: 3
---

@@

## Abstract

In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes. Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups. The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics. This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years.

# 1 Introduction

@@

# 2 Data

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-totalsum-graph
#| fig-cap: "Number of Reported Victims of Crimes in Different Age Groups Over the Years"

@@

Graph 1 (@fig-totalsum-graph) corresponds to the information presented in table 1 (@tbl-totalsum-table). Visualizing the data by age group across each year reveals that the majority of reported crime victims fall into the "Adult" category. Notably, the bars exhibit an ascending trend from 2014 to 2018. However, a conspicuous drop in reported crimes is observed between 2019 and 2020. One plausible explanation for this decline is attributed to the impact of COVID-19, which significantly influenced crime reporting rates during this period.

@@

>>>>

---
title: "Decoding Toronto's Crime Patterns: A Comprehensive Analysis of Victims and Trends (2014-2022)"
author: "Chay Park"
date: today
date-format: long
bibliography: references.bib
abstract: In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes. Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups. The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics. This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years.
format: pdf
editor: visual
prefer-html: true
toc: true
toc-depth: 3
toc-title: Contents
number-sections: true
number-depth: 3
---

@@

# Introduction

@@

# Data

@@

\newpage
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-totalsum-graph
#| fig-cap: "Number of Reported Victims of Crimes in Different Age Groups Over the Years"

@@

# Print the bar plot
print(bar_plot)
```
Graph 1 (@fig-totalsum-graph) corresponds to the information presented in table 1 (@tbl-totalsum-table). Visualizing the data by age group across each year reveals that the majority of reported crime victims fall into the "Adult" category. Notably, the bars exhibit an ascending trend from 2014 to 2018. However, a conspicuous drop in reported crimes is observed between 2019 and 2020. One plausible explanation for this decline is attributed to the impact of COVID-19, which significantly influenced crime reporting rates during this period.

@@

\newpage
